---
title: "01_DataCleanUp"
author: "Katie Heineman"
date: "6/3/2019"
output: html_document
---
# Purpose

Cleaning up data for gap analysis

# Data Import
```{r setup, include=FALSE}
library(data.table)
# Report from Web
data <- fread("Data/CAPR_Collections_Search_Results2019-06-03.csv",na.strings=c("",NULL,NA))

```

# Evaluate missingness of seed counts

```{r seed counts}
data[(`Seed Count`=='' | is.na(`Seed Count`) )& `Collection Type`=="Seed", .(Count=.N),by=c("Primary Seed Bank")]
```

*UCSC* - Seed counts are no where in the UCSC freezer storage records sent in 2018. I should reach out to them again, and see if most of these records are represented in Rancho's database eventually.
*UCB* - I have the seed counts for the 2018 data from UCB, but the accession up to July 2017 seem to have this info in the comments (perhaps maternal lines too) I can make a pass at programming this. Side note, I probably need to ask Vanessa for a full accessions print out bc I might be miss a few things from the second half of July 2018 




