---
title: "02_PhyogeneticTreeBuilding"
author: "Katie Heineman"
date: "6/17/2019"
output: html_document
---

# Set Up
```{r dataimport}
library(data.table)
library(stringr)
library(readr)
# Phylomaker code will not work without this package 
library(phytools)
library(R.utils)
library(ape)
#devtools::install_github("jinyizju/V.PhyloMaker")
library(V.PhyloMaker)
# package for adding subspecies ot species
library(pastis)
library(ips)


# Capitlize first letter of string
firstup <- function(x) {
  substr(x, 1, 1) <- toupper(substr(x, 1, 1))
  x
}

# Loading CaPR Accessions Data
data <- fread("Data/CAPR_Collections_Search_Results2019-06-20.csv")
data[,genus:=word(`Taxon Name (Jepson)`,1,1)]
```


## Matching Genera to the V Phylomaker Super Tree

To have as much phylogenetic resolution as possible, we want to the genera from our species list (Jepson) to specify under "genus.relative" the most closely related genera in the Phylomaker Super Tree. I did this manually for about 128 genera and I have indicated for each match the citation key for th reference in my Zotero Library. This tree differs significantly from the super tree used in S Phylomaker. I have another file with that data clean up (which I did first)


```{r v phylo maker data clean up}
###################### V Phylomaker  ########################


## Making species list for CaPR species
Spp1 <- data[,.(Count=.N),by="Taxon Name (Jepson)"]
Spp1[,genus:=word(`Taxon Name (Jepson)`,1,1),by="Taxon Name (Jepson)"]

## Finding Family's from genera from phylomaker Nodes file
genusTable1 = as.data.table(nodes.info.1)[,.(family=family[1]),by="genus"]

## Merge megatree families onto genera
Spp1 <- merge(Spp1,genusTable1,by="genus",all.x=T)
setnames(Spp1,"Taxon Name (Jepson)","species")
Spp1 <- Spp1[,.(species,genus,family)]

# Which genera weren't matched in the mega tree
GenNa1 <- Spp1[is.na(family),.(Count=.N),by="genus"]
JepFam1 <- data[,.(Count=.N),by=c("Family","genus")]
# Adding families to genera that weren't matched in the super tree
GenNa1 <- merge(GenNa1,JepFam1, by="genus")
GenNa1[,Count.x:=NULL]
GenNa1[,Count.y:=NULL]
GenNa1[,Family:=firstup(tolower(Family))]
# Checking which families in the CaPR list are not in the super tree
GenNa1[!(Family%in%genusTable1$family)][order(Family)]

# Making a few fixes to these famileis
GenNa1[Family=="Agavaceae", Family:="Asparagacaeae"]
GenNa1[Family=="Chenopodiaceae", Family:="Amaranthaceae"]

GenNa1[!(Family%in%genusTable1$family),Family:="FernOrNonVascular"]


# Assigning Genus Relatives
GenNa1[genus%in%c("Acanthoscyphus","Oxytheca"), `:=` (genus.relative="Sidotheca",citation="Reveal_JohanneshowelliaPolygonaceaeEriogonoideae_2004")]
GenNa1[genus%in%c("Achyrachaena"), `:=` (genus.relative="Blepharipappus",citation="Baldwin_Originrelationshipstarweedsilversword_2000")]
GenNa1[genus%in%c("Achyronychia"), `:=` (genus.relative="Loeflingia",citation="Greenberg_Molecularsystematicscharacter_2011")]
GenNa1[genus%in%c("Aconogonon"), `:=` (genus.relative="Polygonum",citation="ThePlantList")]
GenNa1[genus%in%c("Allotropa"), `:=` (genus.relative="Monotropa",citation="Cullings_MolecularphylogenyMonotropoideae_1994")]
GenNa1[genus%in%c("Ammoselinum","Apiastrum"), `:=` (genus.relative="Spermolepis",citation="Nesom_TaxonomyApiastrumammoselinum_2012")]
GenNa1[genus%in%c("Amphipappus"), `:=` (genus.relative="Chrysothamnus",citation="Roberts_MolecularPhylogenyChrysothamnus_2004")]
GenNa1[genus%in%c("Amsonia"), `:=` (genus.relative="Melodinus",citation="Simoes_PHYLOGENYSYSTEMATICSRAUVOLFIOIDEAE_2007")]
GenNa1[genus%in%c("Ancistrocarphus"), `:=` (genus.relative="Stylocline",citation="Morefield_THREENEWSPECIES_1992")]
GenNa1[genus%in%c("Argyrochosma"), `:=` (genus.relative="Pellaea",citation="Sigel_Speciesrelationshipsfarina_2011")]
GenNa1[genus%in%c("Aristocapsa"), `:=` (genus.relative="Chorizanthe",citation="Reveal_JohanneshowelliaPolygonaceaeEriogonoideae_2004")]
GenNa1[genus%in%c("Aspidotis","Astrolepis"), `:=` (genus.relative="Cheilanthes",citation="Gastony_CheilanthoidFernsPteridaceae_1998")]
GenNa1[genus%in%c("Bahiopsis","Heliomeris"), `:=` (genus.relative="Viguiera",citation="Schilling_TAXONOMICREVISIONVIGUIERA_1990")]
GenNa1[genus%in%c("Bebbia"), `:=` (genus.relative="Tridax",citation="Panero_Phylogeneticrelationshipssubtribe_1999")]
GenNa1[genus%in%c("Botrypus","Sceptridium"), `:=` (genus.relative="Botrychium",citation="Dauphin_Molecularphylogeneticssupports_2014")]
GenNa1[genus%in%c("Callitriche"), `:=` (genus.relative="Hippuris",citation="Albach_Piecingtogethernew_2005")]
GenNa1[genus%in%c("Callitropsis"), `:=` (genus.relative="Cupressus",citation="ThePlantList")]
GenNa1[genus%in%c("Calyptridium"), `:=` (genus.relative="Cistanthe",citation="Hershkovitz_PhylogeneticAssessmentRevised_1991")]
GenNa1[genus%in%c("Camissoniopsis","Chylismia","Chylismiella"), `:=` (genus.relative="Camissonia",citation="Hershkovitz_PhylogeneticAssessmentRevised_1991")]
GenNa1[genus%in%c("Canbya"), `:=` (genus.relative="Argemone",citation="Jork_MolecularphylogenyOld_1995")]
GenNa1[genus%in%c("Carsonia"), `:=` (genus.relative="Cleome",citation="ThePlantList")]
GenNa1[genus%in%c("Centromadia"), `:=` (genus.relative="Hemizonia",citation="Baldwin_NewCombinationsNew_1999")]
GenNa1[genus%in%c("Centrostegia"), `:=` (genus.relative="Chorizanthe",citation="Reveal_JohanneshowelliaPolygonaceaeEriogonoideae_2004")]
GenNa1[genus%in%c("Chamerion"), `:=` (genus.relative="Epilobium",citation="Levin_ParaphylytribeOnagreae_2004")]
GenNa1[genus%in%c("Chloropyron","Dicranostegia"), `:=` (genus.relative="Cordylanthus",citation="Tank_Phylogeneticclassificationsubtribe_2009")]
GenNa1[genus%in%c("Coleogyne"), `:=` (genus.relative="Kerria",citation="Potter_PhylogenyclassificationRosaceae_2007")]
GenNa1[genus%in%c("Extriplex","Stutzia"), `:=` (genus.relative="Atriplex",citation="Kadereit_MolecularphylogenyAtripliceae_2010")]
GenNa1[genus%in%c("Monolepis"), `:=` (genus.relative="Spinacia",citation="Kadereit_MolecularphylogenyAtripliceae_2010")]
GenNa1[genus%in%c("Orogenia"), `:=` (genus.relative="Lomatium",citation="Sun_ITSBasedPhylogeneticAnalysis_2004a")]
GenNa1[genus%in%c("Sphenosciadium"), `:=` (genus.relative="Angelica",citation="Sun_ITSBasedPhylogeneticAnalysis_2004a")]
GenNa1[genus%in%c("Pilostyles"), `:=` (genus.relative="Apodanthes",citation="Blarer_Comparativefloralstructure_2004")]
GenNa1[genus%in%c("Landoltia"), `:=` (genus.relative="Spirodela",citation="Tippery_Evaluationphylogeneticrelationships_2015")]
GenNa1[genus%in%c("Dicoria","Iva"), `:=` (genus.relative="Xanthium",citation="Miao_SystematicsImplicationsChloroplast_1995")]
GenNa1[genus%in%c("Hymenopappus"), `:=` (genus.relative="Marshallia",citation="Karis_MorphologicalphylogeneticsAsteraceaeAsteroideae_1993")]
GenNa1[genus%in%c("Jensia"), `:=` (genus.relative="Madia",citation="Baldwin_Originrelationshipstarweedsilversword_2000")]
GenNa1[genus%in%c("Malperia"), `:=` (genus.relative="Hofmeisteria",citation="ThePlantList")]
GenNa1[genus%in%c("Phalacroseris"), `:=` (genus.relative="Krigia",citation="Lee_PhylogeneticRelationshipsPrimarily_2003")]
GenNa1[genus%in%c("Rudbeckia"), `:=` (genus.relative="Helianthus",citation="Urbatsch_PhylogeneticAffinitiesConeflower_1995")]
GenNa1[genus%in%c("Sanvitalia"), `:=` (genus.relative="Zaluzania",citation="Panero_Phylogeneticrelationshipssubtribe_1999")]
GenNa1[genus%in%c("Stebbinsoseris"), `:=` (genus.relative="Microseris",citation="Panero_Phylogeneticrelationshipssubtribe_1999")]
GenNa1[genus%in%c("Verbesina"), `:=` (genus.relative="Encelia",citation="Panero_Chloroplastdnarestriction_1997")]
GenNa1[genus%in%c("Struthiopteris","Woodwardia"), `:=` (genus.relative="Sadleria",citation="deGasper_Molecularphylogenyfern_2017")]
GenNa1[genus%in%c("Eucrypta"), `:=` (genus.relative="Phacelia",citation="Ferguson_PhylogeneticAnalysisRelationships_1998")]
GenNa1[genus%in%c("Howellanthus"), `:=` (genus.relative="Phacelia",citation="Gilbert_PhylogeneticRelationshipsPhacelia_2005")]
GenNa1[genus%in%c("Idahoa","Subularia"), `:=` (genus.relative="Xerodraba",citation="Warwick_Closinggapsphylogenetic_2010")]
GenNa1[genus%in%c("Transberingia"), `:=` (genus.relative="Crucihimalaya",citation="Bailey_GlobalPhylogenyBrassicaceae_2006")]
GenNa1[genus%in%c("Grusonia"), `:=` (genus.relative="Corynopuntia",citation="Griffith_PhylogenyOpuntioideaeCactaceae_2009")]
GenNa1[genus%in%c("Githopsis"), `:=` (genus.relative="Heterocodon",citation="Zhou_Phylogeneticassessmentbiogeographic_2012")]
GenNa1[genus%in%c("Howellia","Porterella","Legenere"), `:=` (genus.relative="Downingia",citation="Schultheis_SystematicsDowningiaCampanulaceae_2001")]
GenNa1[genus%in%c("Nemacladus"), `:=` (genus.relative="Campanula",citation="Cosner_PhylogeneticrelationshipsCampanulales_1994")]
GenNa1[genus%in%c("Triodanis"), `:=` (genus.relative="Legousia",citation="Cosner_ChloroplastDNArearrangements_2004")]
GenNa1[genus%in%c("Scopulophila"), `:=` (genus.relative="Drymaria",citation="Smissen_SubfamilialrelationshipsCaryophyllaceae_2002")]
GenNa1[genus%in%c("Crocanthemum"), `:=` (genus.relative="Cistus",citation="Aparicio_Phylogeneticreconstructiongenus_2017")]
GenNa1[genus%in%c("Oxystylis","Peritoma","Wislizenia"), `:=` (genus.relative="Cleomella",citation="Riser_PhylogeneticrelationshipsNorth_2013")]
GenNa1[genus%in%c("Sedella"), `:=` (genus.relative="Sedum",citation="Nikulin_PhylogeneticrelationshipsSedum_2016")]
GenNa1[genus%in%c("Hesperocyparis"), `:=` (genus.relative="Cupressus",citation="ThePlantList")]
GenNa1[genus%in%c("Hemitomes"), `:=` (genus.relative="Monotropa",citation="Cullings_Singlephylogeneticorigin_1996")]
GenNa1[genus%in%c("Pityopus","Pterospora"), `:=` (genus.relative="Pleuricospora",citation="Cullings_Singlephylogeneticorigin_1996")]
GenNa1[genus%in%c("Sarcodes"), `:=` (genus.relative="Monotropa",citation="Kron_PhylogeneticRelationshipsEmpetraceae_1996")]
GenNa1[genus%in%c("Hosackia"), `:=` (genus.relative="Lotus",citation="Allan_Tribaldelimitationphylogenetic_2000")]
GenNa1[genus%in%c("Pickeringia"), `:=` (genus.relative="Styphnolobium",citation="Wojciechowski_PhylogenyLegumesLeguminosae_2004")]
GenNa1[genus%in%c("Notholithocarpus"), `:=` (genus.relative="Quercus",citation="Manos_Phylogeneticrelationshipstaxonomic_2008")]
GenNa1[genus%in%c("Comastoma"), `:=` (genus.relative="Gentianella",citation="vonHagen_Phylogenyflowerevolution_2002")]
GenNa1[genus%in%c("Frasera"), `:=` (genus.relative="Swertia",citation="vonHagen_Phylogenyflowerevolution_2002")]
GenNa1[genus%in%c("Eustoma","Zeltnera"), `:=` (genus.relative="Sabatia",citation="Mansion_Genericdelimitationphylogenetic_2004")]
GenNa1[genus%in%c("Condea"), `:=` (genus.relative="Hyptis",citation="Mansion_Genericdelimitationphylogenetic_2004")]
GenNa1[genus%in%c("Trichostema"), `:=` (genus.relative="Caryopteris",citation="Wagstaff_PhylogenyLabiataeinferred_1998")]
GenNa1[genus%in%c("Streptopus"), `:=` (genus.relative="Prosartes",citation="Fay_PhylogeneticsLilliales_2006")]
GenNa1[genus%in%c("Floerkea"), `:=` (genus.relative="Limnanthes",citation="Meyers_molecularphylogenyLimnanthes_2010")]
GenNa1[genus%in%c("Herissantia"), `:=` (genus.relative="Abutilon",citation="Tate_Phylogeneticrelationshipstribe_2005")]
GenNa1[genus%in%c("Iliamna","Malacothamnus"), `:=` (genus.relative="Alcea",citation="LaDuke_ChloroplastDNABased_1995")]
GenNa1[genus%in%c("Sidalcea"), `:=` (genus.relative="Eremalche",citation="Tate_Phylogeneticrelationshipstribe_2005")]
GenNa1[genus%in%c("Tripterocalyx"), `:=` (genus.relative="Abronia",citation="Douglas_MolecularphylogenyNyctaginaceae_2007")]
GenNa1[genus%in%c("Eremothera","Eulobus"), `:=` (genus.relative="Camissonia",citation="Levin_ParaphylytribeOnagreae_2004")]
GenNa1[genus%in%c("Neoholmgrenia","Tetrapteron"), `:=` (genus.relative="Camissonia",citation="Allen_PhylogeneticModelsLinking_2017")]
GenNa1[genus%in%c("Taraxia"), `:=` (genus.relative="Gayophytum",citation="Allen_PhylogeneticModelsLinking_2017")]
GenNa1[genus%in%c("Listera"), `:=` (genus.relative="Vanda",citation="Neyland_PhylogenySubfamilyEpidendroideae_1996")]
GenNa1[genus%in%c("Piperia"), `:=` (genus.relative="Platanthera",citation="Bateman_Molecularphylogeneticsmorphological_2009")]
GenNa1[genus%in%c("Kopsiopsis"), `:=` (genus.relative="Boschniakia",citation="McNeal_Phylogenyoriginsholoparasitism_2013")]
GenNa1[genus%in%c("Meconella"), `:=` (genus.relative="Roemeria",citation="Kadereit_phylogenyPapaverPapaveraceae_1997")]
GenNa1[genus%in%c("Gambelia"), `:=` (genus.relative="Galvezia",citation="Ogutcen_phylogeneticstudytribe_2016")]
GenNa1[genus%in%c("Holmgrenanthe"), `:=` (genus.relative="Asarina",citation="Ghebrehiwet_PhylogenytribeAntirrhineae_2000")]
GenNa1[genus%in%c("Lindernia"), `:=` (genus.relative="Scrophularia",citation="Estes_Phylogeneticrelationshipsmonotypic_2008")]
GenNa1[genus%in%c("Maurandya"), `:=` (genus.relative="Maurandya",citation="Ogutcen_phylogeneticstudytribe_2016")]
GenNa1[genus%in%c("Nuttallanthus"), `:=` (genus.relative="Linaria",citation="Crawford_Geneticvariationreproductive_2006")]
GenNa1[genus%in%c("Pseudorontium"), `:=` (genus.relative="Antirrhinum",citation="Keil_MOHAVEASUBSUMEDANTIRRHINUM_2018")]
GenNa1[genus%in%c("Tonella"), `:=` (genus.relative="Collinsia",citation="Baldwin_Phylogeneticperspectivesdiversification_2011")]
GenNa1[genus%in%c("Dasyochloa"), `:=` (genus.relative="Munroa",citation="Columbus_PhylogeneticsChloridoideaeGramineae_2007")]
GenNa1[genus%in%c("Dissanthelium"), `:=` (genus.relative="Poa",citation="Columbus_PhylogeneticsChloridoideaeGramineae_2007")]
GenNa1[genus%in%c("Scribneria"), `:=` (genus.relative="Deschampsia",citation="Soreng_worldwidephylogeneticclassification_2017")]
GenNa1[genus%in%c("Torreyochloa"), `:=` (genus.relative="Deschampsia",citation="Soreng_phylogeneticanalyischloroplast_1990")]
GenNa1[genus%in%c("Vahlodea"), `:=` (genus.relative="Deschampsia",citation="Chiapella_MolecularPhylogeneticStudy_2007")]
GenNa1[genus%in%c("Aconogonon"), `:=` (genus.relative="Koenigia",citation="Galasso_MolecularphylogenyPolygonum_2009")]
GenNa1[genus%in%c("Mucronea"), `:=` (genus.relative="Chorizanthe",citation="Kempton_SystematicsEriogonoideaePolygonaceae_2012")]
GenNa1[genus%in%c("Nemacaulis"), `:=` (genus.relative="Chorizanthe",citation="Kempton_SystematicsEriogonoideaePolygonaceae_2012")]
GenNa1[genus%in%c("Rumex"), `:=` (genus.relative="Rheum",citation="Schuster_updatedmolecularphylogeny_2015")]
GenNa1[genus%in%c("Systenotheca"), `:=` (genus.relative="Chorizanthe",citation="Kempton_SystematicsEriogonoideaePolygonaceae_2012")]
GenNa1[genus%in%c("Myriopteris"), `:=` (genus.relative="Cheilanthes",citation="Grusz_monophyleticCheilanthesresurrection_2013")]
GenNa1[genus%in%c("Notholaena"), `:=` (genus.relative="Cheilanthes",citation="Rothfels_MonophyleticNotholaenaPteridaceae_2008")]
GenNa1[genus%in%c("Pentagramma"), `:=` (genus.relative="Pityrogramma",citation="Schuettpelz_unifiedapproachtaxonomic_2015")]
GenNa1[genus%in%c("Poteridium"), `:=` (genus.relative="Sanguisorba",citation="Potter_PhylogenyclassificationRosaceae_2007")]
GenNa1[genus%in%c("Hemieva"), `:=` (genus.relative="Suksdorfia",citation="Soltis_KaryotypesRelationshipsBolandra_1987")]
GenNa1[genus%in%c("Mitellastra"), `:=` (genus.relative="Elmera",citation="Okuyama_Parallelfloraladaptations_2008")]
GenNa1[genus%in%c("Ozomelis"), `:=` (genus.relative="Conimitella",citation="Folk_Phylogeneticrelationshipscharacter_2014")]
GenNa1[genus%in%c("Pectiantia"), `:=` (genus.relative="Mitella",citation="Folk_Phylogeneticrelationshipscharacter_2014")]
GenNa1[genus%in%c("Euphrosyne"), `:=` (genus.relative="Ambrosia",citation="Miao_SystematicsImplicationsChloroplast_1995")]
GenNa1[genus%in%c("Spartina"), `:=` (genus.relative="Sporobolus",citation="Hilu_phylogenyChloridoideaePoaceae_2001")]

# Update familes in the mega tree list
setkey(Spp1, genus)
setkey(GenNa1, genus)
Spp1[GenNa1,`:=` (genus = i.genus,family=i.Family, genus.relative=i.genus.relative)]

# Adding species relatives to varieties and subspecies
Spp1[grepl("var.",species, fixed=T) | grepl("subsp.",species, fixed=T),species.relative:=word(species,1,2)]

# Limit to Vascular Plants
SppVas1 <- Spp1[family!="FernOrNonVascular"]

```

# Looking at how V Phylomaker Binds Species with Abies as example genus

I specified that Abies magnifica var. magnifica and var. shastensis are relatives of Abies magnifica. 

```{r abies example}

abiesBound <- bind.relative(Spp1[genus=="Abies"])
result_california_treeV_abies<- phylo.maker(sp.list=abiesBound$species.list, tree=abiesBound$phylo, nodes=abiesBound$nodes.info) 
plot(result_california_treeV_abies$scenario.3)

```

# Playing with Pastis
```{r pastis}

SppCopy <- SppVas1
SppCopy[,binomial:=word(species,1,2)]
SppCopy[,SppCount:=.N,by="binomial"]
SppCopy[,SppID:=1:.N,by="binomial"]
SppOnly <- SppCopy[SppID==1]
SppOnly[SppCount==1,species:=binomial]

SppOnly <- SppOnly[,.(species=binomial, genus=genus,family=family, genus.relative=genus.relative,species.relative=species.relative)]
abiesBoundSppOnly <- bind.relative(as.data.frame(SppOnly[genus=="Abies"]))

plot(abiesBoundSppOnly$phylo)

abiesList = SppCopy[genus=="Abies",.(taxon=species,clade=binomial)]
abiesList[,clade:=gsub(" ", "_",clade)]
abiesList[,taxon:=gsub(" ", "_",taxon)]
abiesList[taxon=="Abies_lasiocarpa_var._lasiocarpa",taxon:="Abies_lasiocarpa"]


obj <- pastis_main(constraint_tree=abiesBoundSppOnly$phylo,taxa_list=as.data.frame(abiesList),output_file="MrBayesData/ABIES.nexus")

system("mb MrBayesData/ABIES.nexus")
execute <- system("execute MrBayesData/ABIES.nexus")

abiesTreeMCMC <- read.nexus("MrBayesData/ABIES.nexus.con.tre")

plot(abiesTreeMCMC)

# conch(constraint_tree=abiesBoundSppOnly$phylo,
# mrbayes_output='ABIES.nexus.t',
# simple_edge_scaling=TRUE)



```

# Assembling the Phylogenetic Tree with V Phylomaker

V.Phylomater produces phylogenies using three scenarios. This function & method were described in Qian & Jin 2019 in Journal of Ecology.

1. adding genera or species as basal polytomies within their families or genera 
2. adding genera or species randomly within their families or genera 
3. adding genera or species to their families or genera using the same approach implemented in Phylomatic and BLADJ  <- This is deafult



```{r vphylomaker}
# sourcing V Phylomaker code
# sapply( list.files("VPhylomakerCodes/", full.names=TRUE), source )



## Bulding Tree for Scenario 3


write.tree(result_california_treeV_new$scenario.3,"Data/phyloVCali_genusNotCorrected_devtoolsVersion.tre")
write.tree(result_california_treeV$scenario.3,"Data/phyloVCali_genusNotCorrected.tre")
plot.phylo(result_california_treeV$scenario.3,type="fan",cex=0.3)

treeTest <- read.tree("Data/phyloVCali_genusNotCorrected_devtoolsVersion.tre")

```