---
title: "02_PhyogeneticTreeBuilding"
author: "Katie Heineman"
date: "6/17/2019"
output: html_document
---

# Set Up
```{r dataimport}
library(data.table)
library(stringr)
library(readr)
# Phylomaker code will not work without this package 
library(phytools)
library(R.utils)
library(ape)
#devtools::install_github("jinyizju/V.PhyloMaker")
library(V.PhyloMaker)


# Capitlize first letter of string
firstup <- function(x) {
  substr(x, 1, 1) <- toupper(substr(x, 1, 1))
  x
}

# Loading data
data <- fread("Data/CAPR_Collections_Search_Results2019-06-03.csv")
data[,genus:=word(`Taxon Name (Jepson)`,1,1)]
```

# Matching Genera and Families to Phylomaker Super Tree

To have as much phylogenetic resolution as possible, we want to the genera from our species list (Jepson) to match the synonymous genera in the Phylomaker Super tree. I did this manually for about 150 genera. I was able to reassign about 91 genera. The rest that do not have obvious synonyms will be matched at family level.

```{r phylogenetic tree building}

############ S Phylomaker  #############
## Read in the megaphylogeny in S Phylomaker
phylo<-read.tree("Data/PhytoPhylo.tre") # read in the megaphylogeny.
nodes <- as.data.table(read_delim("Data/nodes.csv", "\t", escape_double = FALSE,  trim_ws = TRUE))
 
## Making species list for CaPR species
Spp <- data[,.(Count=.N),by="Taxon Name (Jepson)"]
Spp[,genus:=word(`Taxon Name (Jepson)`,1,1),by="Taxon Name (Jepson)"]

## Finding Family's from genera from phylomaker Nodes file
genusTable = nodes[,.(family=family[1]),by="genus"]

## Merge megatree families onto genera
Spp <- merge(Spp,genusTable,by="genus",all.x=T)
#Spp[genus=="Eremanthus", family:="Asteraceae"]
setnames(Spp,"Taxon Name (Jepson)","species")
Spp <- Spp[,.(species,genus,family)]

# Which genera weren't matched in the mega tree
GenNa <- Spp[is.na(family),.(Count=.N),by="genus"]
JepFam <- data[,.(Count=.N),by=c("Family","genus")]
# Adding families to genera that weren't matched in the super tree
GenNa <- merge(GenNa,JepFam, by="genus")
GenNa[,Count.x:=NULL]
GenNa[,Count.y:=NULL]
GenNa[,Family:=firstup(tolower(Family))]
# Checking which families in the CaPR list are not in the super tree
GenNa[!(Family%in%genusTable$family)][order(Family)]

# Making a few fixes to these famileis
GenNa[Family=="Agavaceae", Family:="Asparagacaeae"]
GenNa[Family=="Chenopodiaceae", Family:="Amaranthaceae"]
GenNa[!(Family%in%genusTable$family),Family:="FernOrNonVascular"]

# Matching genera from CaPR list to genera in the super tree
GenNa[genus=="Atrichoseris", genus:="Malacothrix"]
GenNa[genus=="Aristocapsa", genus:="Chorizanthe"]
GenNa[genus=="Benitoa", genus:="Lessingia"]
GenNa[genus=="Bergerocactus", genus:="Cereus"]
GenNa[genus=="Calliscirpus", genus:="Scirpus"]
GenNa[genus=="Callitropsis", genus:="Cupressus"]
GenNa[genus=="Carlquistia", genus:="Raillardella"]
GenNa[genus=="Carsonia", genus:="Cleome"]
GenNa[genus=="Cascadia", genus:="Saxifraga"]
GenNa[genus=="Centrostegia", genus:="Chorizanthe"]
GenNa[genus=="Chloracantha", genus:="Aster"]
GenNa[genus=="Chloropyron", genus:="Cordylanthus"]
GenNa[genus=="Chylismiella", genus:="Camissonia"]
GenNa[genus=="Condea", genus:="Hyptis"]
GenNa[genus=="Crocanthemum", genus:="Halimium"]
GenNa[genus=="Cuniculotinus", genus:="Petradoria"]
GenNa[genus=="Dasyochloa", genus:="Erioneuron"]
GenNa[genus=="Dicranostegia", genus:="Cordylanthus"]
GenNa[genus=="Diplacus", genus:="Mimulus"]
GenNa[genus=="Dodecahema", genus:="Chorizanthe"]
GenNa[genus=="Eremothera", genus:="Camissonia"]
GenNa[genus=="Erythranthe", genus:="Mimulus"]
GenNa[genus=="Eucephalus", genus:="Aster"]
GenNa[genus=="Euphrosyne", genus:="Iva"]
GenNa[genus=="Extriplex", genus:="Atriplex"]
GenNa[genus=="Gamochaeta", genus:="Gnaphalium"]
GenNa[genus=="Greeneocharis", genus:="Cryptantha"]
GenNa[genus=="Grusonia", genus:="Opuntia"]
GenNa[genus=="Harmonia", genus:="Madia"]
GenNa[genus=="Heliomeris", genus:="Viguiera"]
GenNa[genus=="Hemizonella", genus:="Madia"]
GenNa[genus=="Hemizonia", genus:="Deinandra"]
GenNa[genus=="Herissantia", genus:="Abutilon"]
GenNa[genus=="Hesperocyparis", genus:="Cupressus"]
GenNa[genus=="Horkeliella", genus:="Potentilla"]
GenNa[genus=="Horsfordia", genus:="Abutilon"]
GenNa[genus=="Howellanthus", genus:="Phacelia"]
GenNa[genus=="Ionactis", genus:="Aster"]
GenNa[genus=="Ivesia", genus:="Potentilla"]
GenNa[genus=="Jensia", genus:="Madia"]
GenNa[genus=="Johnstonella", genus:="Cryptantha"]
GenNa[genus=="Kochia", genus:="Bassia"]
GenNa[genus=="Kyhosia", genus:="Madia"]
GenNa[genus=="Landoltia", genus:="Spirodela"]
GenNa[genus=="Lastarriaea", genus:="Chorizanthe"]
GenNa[genus=="Lathrocasis", genus:="Gilia"]
GenNa[genus=="Lepidospartum", genus:="Baccharis"]
GenNa[genus=="Leptosyne", genus:="Coreopsis"]
GenNa[genus=="Leucosyris", genus:="Machaeranthera"]
GenNa[genus=="Listera", genus:="Neottia"]
GenNa[genus=="Malvella", genus:="Sida"]
GenNa[genus=="Maurandella", genus:="Maurandya"]
GenNa[genus=="Micromonolepis", genus:="Monolepis"]
GenNa[genus=="Mitellastra", genus:="Mitella"]
GenNa[genus=="Mucronea", genus:="Chorizanthe"]
GenNa[genus=="Munroa", genus:="Crypsis"]
GenNa[genus=="Munzothamnus", genus:="Stephanomeria"]
GenNa[genus=="Neoholmgrenia", genus:="Camissonia"]
GenNa[genus=="Noccaea", genus:="Thlaspi"]
GenNa[genus=="Oreocarya", genus:="Cryptantha"]
GenNa[genus=="Oreostemma", genus:="Aster"]
GenNa[genus=="Osmadenia", genus:="Calycadenia"]
GenNa[genus=="Oxytheca", genus:="Eriogonum"]
GenNa[genus=="Pediomelum", genus:="Psoralea"]
GenNa[genus=="Pentachaeta", genus:="Chaetopappa"]
GenNa[genus=="Picradeniopsis", genus:="Bahia"]
GenNa[genus=="Piperia", genus:="Platanthera"]
GenNa[genus=="Pityopus", genus:="Monotropa"]
GenNa[genus=="Pleurocoronis", genus:="Hofmeisteria"]
GenNa[genus=="Podistera", genus:="Ligusticum"]
GenNa[genus=="Poteridium", genus:="Sanguisorba"]
GenNa[genus=="Pseudorontium", genus:="Antirrhinum"]
GenNa[genus=="Sabulina", genus:="Minuartia"]
GenNa[genus=="Saxifragopsis", genus:="Saxifraga"]
GenNa[genus=="Sclerocactus", genus:="Echinocactus"]
GenNa[genus=="Scopulophila", genus:="Achyronychia"]
GenNa[genus=="Scribneria", genus:="Lepturus"]
GenNa[genus=="Sericocarpus", genus:="Aster"]
GenNa[genus=="Sibara", genus:="Arabis"]
GenNa[genus=="Spermolepis", genus:="Apium"]
GenNa[genus=="Sphaeromeria", genus:="Tanacetum"]
GenNa[genus=="Stebbinsoseris", genus:="Microseris"]
GenNa[genus=="Stutzia", genus:="Atriplex"]
GenNa[genus=="Systenotheca", genus:="Chorizanthe"]
GenNa[genus=="Taraxia", genus:="Camissonia"]
GenNa[genus=="Tetraneuris", genus:="Hymenoxys"]
GenNa[genus=="Tetrapteron", genus:="Camissonia"]
GenNa[genus=="Tonestus", genus:="Haplopappus"]
GenNa[genus=="Transberingia", genus:="Halimolobos"]
GenNa[genus=="Tripterocalyx", genus:="Abronia"]
GenNa[genus=="Vahlodea", genus:="Aira"]
GenNa[genus=="Yabea", genus:="Caucalis"]

# Update familes in the mega tree list
setkey(Spp, genus)
setkey(GenNa, genus)
Spp[GenNa,`:=` (genus = i.genus,family=i.Family)]

# Limit to Vascular Plants
SppVas <- Spp[family!="FernOrNonVascular"]
#############  #############  #############  #############  #############


###################### V Phylomaker  ########################
## Read in the megaphylogeny in S Phylomaker
myenv <- new.env()
GBOTB.extended<-load("Data/GBOTB.extended.rda",env=myenv) # read in the megaphylogeny.
GBOTB.extended <- myenv$GBOTB.extended
nodes.info.1 <- load("Data/nodes.info.1.rda",env=myenv)
nodes.info.1 <- as.data.table(myenv$nodes.info.1)


## Making species list for CaPR species
Spp1 <- data[,.(Count=.N),by="Taxon Name (Jepson)"]
Spp1[,genus:=word(`Taxon Name (Jepson)`,1,1),by="Taxon Name (Jepson)"]

## Finding Family's from genera from phylomaker Nodes file
genusTable1 = nodes.info.1[,.(family=family[1]),by="genus"]

## Merge megatree families onto genera
Spp1 <- merge(Spp1,genusTable1,by="genus",all.x=T)
setnames(Spp1,"Taxon Name (Jepson)","species")
Spp1 <- Spp1[,.(species,genus,family)]

# Which genera weren't matched in the mega tree
GenNa1 <- Spp1[is.na(family),.(Count=.N),by="genus"]
JepFam1 <- data[,.(Count=.N),by=c("Family","genus")]
# Adding families to genera that weren't matched in the super tree
GenNa1 <- merge(GenNa1,JepFam1, by="genus")
GenNa1[,Count.x:=NULL]
GenNa1[,Count.y:=NULL]
GenNa1[,Family:=firstup(tolower(Family))]
# Checking which families in the CaPR list are not in the super tree
GenNa1[!(Family%in%genusTable1$family)][order(Family)]

# Making a few fixes to these famileis
GenNa1[Family=="Agavaceae", Family:="Asparagacaeae"]
GenNa1[Family=="Chenopodiaceae", Family:="Amaranthaceae"]
GenNa1[!(Family%in%genusTable1$family),Family:="FernOrNonVascular"]

# Assigning Genus Relatives
GenNa1[genus%in%c("Acanthoscyphus","Oxytheca"), `:=` (genus.relative="Sidotheca",citation="Reveal_JohanneshowelliaPolygonaceaeEriogonoideae_2004")]
GenNa1[genus%in%c("Achyrachaena"), `:=` (genus.relative="Blepharipappus",citation="Baldwin_Originrelationshipstarweedsilversword_2000")]
GenNa1[genus%in%c("Achyronychia"), `:=` (genus.relative="Loeflingia",citation="Greenberg_Molecularsystematicscharacter_2011")]
GenNa1[genus%in%c("Aconogonon"), `:=` (genus.relative="Polygonum",citation="ThePlantList")]
GenNa1[genus%in%c("Allotropa"), `:=` (genus.relative="Monotropa",citation="Cullings_MolecularphylogenyMonotropoideae_1994")]
GenNa1[genus%in%c("Ammoselinum","Apiastrum"), `:=` (genus.relative="Spermolepis",citation="Nesom_TaxonomyApiastrumammoselinum_2012")]
GenNa1[genus%in%c("Amphipappus"), `:=` (genus.relative="Chrysothamnus",citation="Roberts_MolecularPhylogenyChrysothamnus_2004")]
GenNa1[genus%in%c("Amsonia"), `:=` (genus.relative="Melodinus",citation="Simoes_PHYLOGENYSYSTEMATICSRAUVOLFIOIDEAE_2007")]
GenNa1[genus%in%c("Ancistrocarphus"), `:=` (genus.relative="Stylocline",citation="Morefield_THREENEWSPECIES_1992")]
GenNa1[genus%in%c("Argyrochosma"), `:=` (genus.relative="Pellaea",citation="Sigel_Speciesrelationshipsfarina_2011")]
GenNa1[genus%in%c("Aristocapsa"), `:=` (genus.relative="Chorizanthe",citation="Reveal_JohanneshowelliaPolygonaceaeEriogonoideae_2004")]
GenNa1[genus%in%c("Aspidotis","Astrolepis"), `:=` (genus.relative="Cheilanthes",citation="Gastony_CheilanthoidFernsPteridaceae_1998")]
GenNa1[genus%in%c("Bahiopsis","Heliomeris"), `:=` (genus.relative="Viguiera",citation="Schilling_TAXONOMICREVISIONVIGUIERA_1990")]
GenNa1[genus%in%c("Bebbia"), `:=` (genus.relative="Tridax",citation="Panero_Phylogeneticrelationshipssubtribe_1999")]
GenNa1[genus%in%c("Botrypus","Sceptridium"), `:=` (genus.relative="Botrychium",citation="Dauphin_Molecularphylogeneticssupports_2014")]
GenNa1[genus%in%c("Callitriche"), `:=` (genus.relative="Hippuris",citation="Albach_Piecingtogethernew_2005")]
GenNa1[genus%in%c("Callitropsis"), `:=` (genus.relative="Cupressus",citation="ThePlantList")]
GenNa1[genus%in%c("Calyptridium"), `:=` (genus.relative="Cistanthe",citation="Hershkovitz_PhylogeneticAssessmentRevised_1991")]
GenNa1[genus%in%c("Camissoniopsis","Chylismia","Chylismiella"), `:=` (genus.relative="Camissonia",citation="Hershkovitz_PhylogeneticAssessmentRevised_1991")]
GenNa1[genus%in%c("Canbya"), `:=` (genus.relative="Argemone",citation="Jork_MolecularphylogenyOld_1995")]
GenNa1[genus%in%c("Carsonia"), `:=` (genus.relative="Cleome",citation="ThePlantList")]
GenNa1[genus%in%c("Centromadia"), `:=` (genus.relative="Hemizonia",citation="Baldwin_NewCombinationsNew_1999")]
GenNa1[genus%in%c("Centrostegia"), `:=` (genus.relative="Chorizanthe",citation="Reveal_JohanneshowelliaPolygonaceaeEriogonoideae_2004")]
GenNa1[genus%in%c("Chamerion"), `:=` (genus.relative="Epilobium",citation="Levin_ParaphylytribeOnagreae_2004")]
GenNa1[genus%in%c("Chloropyron","Dicranostegia"), `:=` (genus.relative="Cordylanthus",citation="Tank_Phylogeneticclassificationsubtribe_2009")]
GenNa1[genus%in%c("Coleogyne"), `:=` (genus.relative="Kerria",citation="Potter_PhylogenyclassificationRosaceae_2007")]
GenNa1[genus%in%c("Extriplex","Stutzia"), `:=` (genus.relative="Atriplex",citation="Kadereit_MolecularphylogenyAtripliceae_2010")]
GenNa1[genus%in%c("Monolepis"), `:=` (genus.relative="Spinacia",citation="Kadereit_MolecularphylogenyAtripliceae_2010")]
GenNa1[genus%in%c("Orogenia"), `:=` (genus.relative="Lomatium",citation="Sun_ITSBasedPhylogeneticAnalysis_2004a")]
GenNa1[genus%in%c("Sphenosciadium"), `:=` (genus.relative="Angelica",citation="Sun_ITSBasedPhylogeneticAnalysis_2004a")]
GenNa1[genus%in%c("Pilostyles"), `:=` (genus.relative="Apodanthes",citation="Blarer_Comparativefloralstructure_2004")]
GenNa1[genus%in%c("Landoltia"), `:=` (genus.relative="Spirodela",citation="Tippery_Evaluationphylogeneticrelationships_2015")]
GenNa1[genus%in%c("Dicoria","Iva"), `:=` (genus.relative="Xanthium",citation="Miao_SystematicsImplicationsChloroplast_1995")]
GenNa1[genus%in%c("Hymenopappus"), `:=` (genus.relative="Marshallia",citation="Karis_MorphologicalphylogeneticsAsteraceaeAsteroideae_1993")]
GenNa1[genus%in%c("Jensia"), `:=` (genus.relative="Madia",citation="Baldwin_Originrelationshipstarweedsilversword_2000")]
GenNa1[genus%in%c("Malperia"), `:=` (genus.relative="Hofmeisteria",citation="ThePlantList")]
GenNa1[genus%in%c("Phalacroseris"), `:=` (genus.relative="Krigia",citation="Lee_PhylogeneticRelationshipsPrimarily_2003")]
GenNa1[genus%in%c("Rudbeckia"), `:=` (genus.relative="Helianthus",citation="Urbatsch_PhylogeneticAffinitiesConeflower_1995")]
GenNa1[genus%in%c("Sanvitalia"), `:=` (genus.relative="Zaluzania",citation="Panero_Phylogeneticrelationshipssubtribe_1999")]
GenNa1[genus%in%c("Stebbinsoseris"), `:=` (genus.relative="Microseris",citation="Panero_Phylogeneticrelationshipssubtribe_1999")]
GenNa1[genus%in%c("Verbesina"), `:=` (genus.relative="Encelia",citation="Panero_Chloroplastdnarestriction_1997")]
GenNa1[genus%in%c("Struthiopteris","Woodwardia"), `:=` (genus.relative="Sadleria",citation="deGasper_Molecularphylogenyfern_2017")]
GenNa1[genus%in%c("Eucrypta"), `:=` (genus.relative="Phacelia",citation="Ferguson_PhylogeneticAnalysisRelationships_1998")]
GenNa1[genus%in%c("Howellanthus"), `:=` (genus.relative="Phacelia",citation="Gilbert_PhylogeneticRelationshipsPhacelia_2005")]
GenNa1[genus%in%c("Idahoa","Subularia"), `:=` (genus.relative="Xerodraba",citation="Warwick_Closinggapsphylogenetic_2010")]
GenNa1[genus%in%c("Transberingia"), `:=` (genus.relative="Crucihimalaya",citation="Bailey_GlobalPhylogenyBrassicaceae_2006")]
GenNa1[genus%in%c("Grusonia"), `:=` (genus.relative="Corynopuntia",citation="Griffith_PhylogenyOpuntioideaeCactaceae_2009")]
GenNa1[genus%in%c("Githopsis"), `:=` (genus.relative="Heterocodon",citation="Zhou_Phylogeneticassessmentbiogeographic_2012")]
GenNa1[genus%in%c("Howellia","Porterella","Legenere"), `:=` (genus.relative="Downingia",citation="Schultheis_SystematicsDowningiaCampanulaceae_2001")]
GenNa1[genus%in%c("Nemacladus"), `:=` (genus.relative="Campanula",citation="Cosner_PhylogeneticrelationshipsCampanulales_1994")]
GenNa1[genus%in%c("Triodanis"), `:=` (genus.relative="Legousia",citation="Cosner_ChloroplastDNArearrangements_2004")]
GenNa1[genus%in%c("Scopulophila"), `:=` (genus.relative="Drymaria",citation="Smissen_SubfamilialrelationshipsCaryophyllaceae_2002")]
GenNa1[genus%in%c("Crocanthemum"), `:=` (genus.relative="Cistus",citation="Aparicio_Phylogeneticreconstructiongenus_2017")]
GenNa1[genus%in%c("Oxystylis","Peritoma","Wislizenia"), `:=` (genus.relative="Cleomella",citation="Riser_PhylogeneticrelationshipsNorth_2013")]
GenNa1[genus%in%c("Sedella"), `:=` (genus.relative="Sedum",citation="Nikulin_PhylogeneticrelationshipsSedum_2016")]
GenNa1[genus%in%c("Hesperocyparis"), `:=` (genus.relative="Cupressus",citation="ThePlantList")]
GenNa1[genus%in%c("Hemitomes"), `:=` (genus.relative="Monotropa",citation="Cullings_Singlephylogeneticorigin_1996")]
GenNa1[genus%in%c("Pityopus","Pterospora"), `:=` (genus.relative="Pleuricospora",citation="Cullings_Singlephylogeneticorigin_1996")]
GenNa1[genus%in%c("Sarcodes"), `:=` (genus.relative="Monotropa",citation="Kron_PhylogeneticRelationshipsEmpetraceae_1996")]
GenNa1[genus%in%c("Hosackia"), `:=` (genus.relative="Lotus",citation="Allan_Tribaldelimitationphylogenetic_2000")]
GenNa1[genus%in%c("Pickeringia"), `:=` (genus.relative="Styphnolobium",citation="Wojciechowski_PhylogenyLegumesLeguminosae_2004")]
GenNa1[genus%in%c("Notholithocarpus"), `:=` (genus.relative="Quercus",citation="Manos_Phylogeneticrelationshipstaxonomic_2008")]
GenNa1[genus%in%c("Comastoma"), `:=` (genus.relative="Gentianella",citation="vonHagen_Phylogenyflowerevolution_2002")]
GenNa1[genus%in%c("Frasera"), `:=` (genus.relative="Swertia",citation="vonHagen_Phylogenyflowerevolution_2002")]
GenNa1[genus%in%c("Eustoma","Zeltnera"), `:=` (genus.relative="Sabatia",citation="Mansion_Genericdelimitationphylogenetic_2004")]
GenNa1[genus%in%c("Condea"), `:=` (genus.relative="Hyptis",citation="Mansion_Genericdelimitationphylogenetic_2004")]
GenNa1[genus%in%c("Trichostema"), `:=` (genus.relative="Caryopteris",citation="Wagstaff_PhylogenyLabiataeinferred_1998")]
GenNa1[genus%in%c("Streptopus"), `:=` (genus.relative="Prosartes",citation="Fay_PhylogeneticsLilliales_2006")]
GenNa1[genus%in%c("Floerkea"), `:=` (genus.relative="Limnanthes",citation="Meyers_molecularphylogenyLimnanthes_2010")]
GenNa1[genus%in%c("Herissantia"), `:=` (genus.relative="Abutilon",citation="Tate_Phylogeneticrelationshipstribe_2005")]
GenNa1[genus%in%c("Iliamna","Malacothamnus"), `:=` (genus.relative="Alcea",citation="LaDuke_ChloroplastDNABased_1995")]
GenNa1[genus%in%c("Sidalcea"), `:=` (genus.relative="Eremalche",citation="Tate_Phylogeneticrelationshipstribe_2005")]
GenNa1[genus%in%c("Tripterocalyx"), `:=` (genus.relative="Abronia",citation="Douglas_MolecularphylogenyNyctaginaceae_2007")]
GenNa1[genus%in%c("Eremothera","Eulobus"), `:=` (genus.relative="Camissonia",citation="Levin_ParaphylytribeOnagreae_2004")]
GenNa1[genus%in%c("Neoholmgrenia","Tetrapteron"), `:=` (genus.relative="Camissonia",citation="Allen_PhylogeneticModelsLinking_2017")]
GenNa1[genus%in%c("Taraxia"), `:=` (genus.relative="Gayophytum",citation="Allen_PhylogeneticModelsLinking_2017")]
GenNa1[genus%in%c("Listera"), `:=` (genus.relative="Vanda",citation="Neyland_PhylogenySubfamilyEpidendroideae_1996")]
GenNa1[genus%in%c("Piperia"), `:=` (genus.relative="Platanthera",citation="Bateman_Molecularphylogeneticsmorphological_2009")]
GenNa1[genus%in%c("Kopsiopsis"), `:=` (genus.relative="Boschniakia",citation="McNeal_Phylogenyoriginsholoparasitism_2013")]
GenNa1[genus%in%c("Meconella"), `:=` (genus.relative="Roemeria",citation="Kadereit_phylogenyPapaverPapaveraceae_1997")]
GenNa1[genus%in%c("Gambelia"), `:=` (genus.relative="Galvezia",citation="Ogutcen_phylogeneticstudytribe_2016")]
GenNa1[genus%in%c("Holmgrenanthe"), `:=` (genus.relative="Asarina",citation="Ghebrehiwet_PhylogenytribeAntirrhineae_2000")]
GenNa1[genus%in%c("Lindernia"), `:=` (genus.relative="Scrophularia",citation="Estes_Phylogeneticrelationshipsmonotypic_2008")]
GenNa1[genus%in%c("Maurandya"), `:=` (genus.relative="Maurandya",citation="Ogutcen_phylogeneticstudytribe_2016")]
GenNa1[genus%in%c("Nuttallanthus"), `:=` (genus.relative="Linaria",citation="Crawford_Geneticvariationreproductive_2006")]
GenNa1[genus%in%c("Pseudorontium"), `:=` (genus.relative="Antirrhinum",citation="Keil_MOHAVEASUBSUMEDANTIRRHINUM_2018")]
GenNa1[genus%in%c("Tonella"), `:=` (genus.relative="Collinsia",citation="Baldwin_Phylogeneticperspectivesdiversification_2011")]
GenNa1[genus%in%c("Dasyochloa"), `:=` (genus.relative="Munroa",citation="Columbus_PhylogeneticsChloridoideaeGramineae_2007")]
GenNa1[genus%in%c("Dissanthelium"), `:=` (genus.relative="Poa",citation="Columbus_PhylogeneticsChloridoideaeGramineae_2007")]
GenNa1[genus%in%c("Scribneria"), `:=` (genus.relative="Deschampsia",citation="Soreng_worldwidephylogeneticclassification_2017")]
GenNa1[genus%in%c("Torreyochloa"), `:=` (genus.relative="Deschampsia",citation="Soreng_phylogeneticanalyischloroplast_1990")]
GenNa1[genus%in%c("Vahlodea"), `:=` (genus.relative="Deschampsia",citation="Chiapella_MolecularPhylogeneticStudy_2007")]
GenNa1[genus%in%c("Aconogonon"), `:=` (genus.relative="Koenigia",citation="Galasso_MolecularphylogenyPolygonum_2009")]
GenNa1[genus%in%c("Mucronea"), `:=` (genus.relative="Chorizanthe",citation="Kempton_SystematicsEriogonoideaePolygonaceae_2012")]
GenNa1[genus%in%c("Nemacaulis"), `:=` (genus.relative="Chorizanthe",citation="Kempton_SystematicsEriogonoideaePolygonaceae_2012")]
GenNa1[genus%in%c("Rumex"), `:=` (genus.relative="Rheum",citation="Schuster_updatedmolecularphylogeny_2015")]
GenNa1[genus%in%c("Systenotheca"), `:=` (genus.relative="Chorizanthe",citation="Kempton_SystematicsEriogonoideaePolygonaceae_2012")]
GenNa1[genus%in%c("Myriopteris"), `:=` (genus.relative="Cheilanthes",citation="Grusz_monophyleticCheilanthesresurrection_2013")]
GenNa1[genus%in%c("Notholaena"), `:=` (genus.relative="Cheilanthes",citation="Rothfels_MonophyleticNotholaenaPteridaceae_2008")]
GenNa1[genus%in%c("Pentagramma"), `:=` (genus.relative="Pityrogramma",citation="Schuettpelz_unifiedapproachtaxonomic_2015")]
GenNa1[genus%in%c("Poteridium"), `:=` (genus.relative="Sanguisorba",citation="Potter_PhylogenyclassificationRosaceae_2007")]
GenNa1[genus%in%c("Hemieva"), `:=` (genus.relative="Suksdorfia",citation="Soltis_KaryotypesRelationshipsBolandra_1987")]
GenNa1[genus%in%c("Mitellastra"), `:=` (genus.relative="Elmera",citation="Okuyama_Parallelfloraladaptations_2008")]
GenNa1[genus%in%c("Ozomelis"), `:=` (genus.relative="Conimitella",citation="Folk_Phylogeneticrelationshipscharacter_2014")]
GenNa1[genus%in%c("Pectiantia"), `:=` (genus.relative="Mitella",citation="Folk_Phylogeneticrelationshipscharacter_2014")]


# Update familes in the mega tree list
setkey(Spp1, genus)
setkey(GenNa1, genus)
Spp1[GenNa1,`:=` (genus = i.genus,family=i.Family)]

# Limit to Vascular Plants
SppVas1 <- Spp1[family!="FernOrNonVascular"]

```

# Assembling the Phylogenetic Tree with S Phylomaker

Using the S Phylomaker Code to construct phylogenetic tree against species list. 

S.Phylomater produces phylogenies using three scenarios. This function & method were described in Qian & Jin 2016 in Journal of Ecology.

1. adding genera or species as basal polytomies within their families or genera 
2. adding genera or species randomly within their families or genera 
3. adding genera or species to their families or genera using the same approach implemented in Phylomatic and BLADJ 

```{r creating the tree}
# Source the code from Qian & Jin 2016 paper
source("R_codes for S.PhyloMaker.R")

## Bulding Tree for all three scenarios
result_california_tree <- S.PhyloMaker(spList=as.data.frame(SppVas), tree=phylo, nodes=nodes, scenarios=c("S3")) 


```


# Assembling the Phylogenetic Tree with V Phylomaker

```{r vphylomaker}
# sourcing V Phylomaker code
# sapply( list.files("VPhylomakerCodes/", full.names=TRUE), source )



## Bulding Tree for Scenario 3
result_california_treeV_new <- phylo.maker(sp.list=as.data.frame(Spp1), tree=GBOTB.extended, nodes=nodes.info.1) 

write.tree(result_california_treeV_new$scenario.3,"Data/phyloVCali_genusNotCorrected_devtoolsVersion.tre")

write.tree(result_california_treeV$scenario.3,"Data/phyloVCali_genusNotCorrected.tre")
plot.phylo(result_california_treeV$scenario.3,type="fan",cex=0.3)

treeTest <- read.tree("Data/phyloVCali_genusNotCorrected_devtoolsVersion.tre")

```