---
title: "02_PhyogeneticTreeBuilding"
author: "Katie Heineman"
date: "6/17/2019"
output: html_document
---

# Setting up Data
```{r dataimport}
library(data.table)
library(stringr)
library(readr)
# Phylomaker code will not work without this package 
library(phytools)

# Capitlize first letter of string
firstup <- function(x) {
  substr(x, 1, 1) <- toupper(substr(x, 1, 1))
  x
}

# Loading data
data <- fread("Data/CAPR_Collections_Search_Results2019-06-03.csv")
data[,genus:=word(`Taxon Name (Jepson)`,1,1)]
```

# Matching Genera and Families to Phylomaker Super Tree

To have as much phylogenetic resolution as possible, we want to the genera from our species list (Jepson) to match the synonymous genera in the Phylomaker Super tree. I did this manually for about 150 genera. 

```{r phylogenetic tree building}
## Practice using the tool with example data
# # Read in the megaphylogeny
 phylo<-read.tree("Data/PhytoPhylo.tre") # read in the megaphylogeny.
 nodes <- as.data.table(read_delim("Data/nodes.csv", "\t", escape_double = FALSE,  trim_ws = TRUE))
 
## Making species list for CaPR species
Spp <- data[,.(Count=.N),by="Taxon Name (Jepson)"]
Spp[,genus:=word(`Taxon Name (Jepson)`,1,1),by="Taxon Name (Jepson)"]

## Finding Family's from genera from phylomaker Nodes file
genusTable = nodes[,.(family=family[1]),by="genus"]

## Merge megatree families onto genera
Spp <- merge(Spp,genusTable,by="genus",all.x=T)
#Spp[genus=="Eremanthus", family:="Asteraceae"]
setnames(Spp,"Taxon Name (Jepson)","species")
Spp <- Spp[,.(species,genus,family)]

# Which genera weren't matched in the mega tree
GenNa <- Spp[is.na(family),.(Count=.N),by="genus"]
JepFam <- data[,.(Count=.N),by=c("Family","genus")]
# Adding families to genera that weren't matched in the super tree
GenNa <- merge(GenNa,JepFam, by="genus")
GenNa[,Count.x:=NULL]
GenNa[,Count.y:=NULL]
GenNa[,Family:=firstup(tolower(Family))]
# Checking which families in the CaPR list are not in the super tree
GenNa[!(Family%in%genusTable$family)][order(Family)]

# Making a few fixes to these famileis
GenNa[Family=="Agavaceae", Family:="Asparagacaeae"]
GenNa[Family=="Chenopodiaceae", Family:="Amaranthaceae"]
GenNa[!(Family%in%genusTable$family),Family:="FernOrNonVascular"]

# Matching genera from CaPR list to genera in the super tree
GenNa[genus=="Atrichoseris", genus:="Malacothrix"]
GenNa[genus=="Aristocapsa", genus:="Chorizanthe"]
GenNa[genus=="Benitoa", genus:="Lessingia"]
GenNa[genus=="Bergerocactus", genus:="Cereus"]
GenNa[genus=="Calliscirpus", genus:="Scirpus"]
GenNa[genus=="Callitropsis", genus:="Cupressus"]
GenNa[genus=="Carlquistia", genus:="Raillardella"]
GenNa[genus=="Carsonia", genus:="Cleome"]
GenNa[genus=="Cascadia", genus:="Saxifraga"]
GenNa[genus=="Centrostegia", genus:="Chorizanthe"]
GenNa[genus=="Chloracantha", genus:="Aster"]
GenNa[genus=="Chloropyron", genus:="Cordylanthus"]
GenNa[genus=="Chylismiella", genus:="Camissonia"]
GenNa[genus=="Condea", genus:="Hyptis"]
GenNa[genus=="Crocanthemum", genus:="Halimium"]
GenNa[genus=="Cuniculotinus", genus:="Petradoria"]
GenNa[genus=="Dasyochloa", genus:="Erioneuron"]
GenNa[genus=="Dicranostegia", genus:="Cordylanthus"]
GenNa[genus=="Diplacus", genus:="Mimulus"]
GenNa[genus=="Dodecahema", genus:="Chorizanthe"]
GenNa[genus=="Eremothera", genus:="Camissonia"]
GenNa[genus=="Erythranthe", genus:="Mimulus"]
GenNa[genus=="Eucephalus", genus:="Aster"]
GenNa[genus=="Euphrosyne", genus:="Iva"]
GenNa[genus=="Extriplex", genus:="Atriplex"]
GenNa[genus=="Gamochaeta", genus:="Gnaphalium"]
GenNa[genus=="Greeneocharis", genus:="Cryptantha"]
GenNa[genus=="Grusonia", genus:="Opuntia"]
GenNa[genus=="Harmonia", genus:="Madia"]
GenNa[genus=="Heliomeris", genus:="Viguiera"]
GenNa[genus=="Hemizonella", genus:="Madia"]
GenNa[genus=="Hemizonia", genus:="Deinandra"]
GenNa[genus=="Herissantia", genus:="Abutilon"]
GenNa[genus=="Hesperocyparis", genus:="Cupressus"]
GenNa[genus=="Horkeliella", genus:="Potentilla"]
GenNa[genus=="Horsfordia", genus:="Abutilon"]
GenNa[genus=="Howellanthus", genus:="Phacelia"]
GenNa[genus=="Ionactis", genus:="Aster"]
GenNa[genus=="Ivesia", genus:="Potentilla"]
GenNa[genus=="Jensia", genus:="Madia"]
GenNa[genus=="Johnstonella", genus:="Cryptantha"]
GenNa[genus=="Kochia", genus:="Bassia"]
GenNa[genus=="Kyhosia", genus:="Madia"]
GenNa[genus=="Landoltia", genus:="Spirodela"]
GenNa[genus=="Lastarriaea", genus:="Chorizanthe"]
GenNa[genus=="Lathrocasis", genus:="Gilia"]
GenNa[genus=="Lepidospartum", genus:="Baccharis"]
GenNa[genus=="Leptosyne", genus:="Coreopsis"]
GenNa[genus=="Leucosyris", genus:="Machaeranthera"]
GenNa[genus=="Listera", genus:="Neottia"]
GenNa[genus=="Malvella", genus:="Sida"]
GenNa[genus=="Maurandella", genus:="Maurandya"]
GenNa[genus=="Micromonolepis", genus:="Monolepis"]
GenNa[genus=="Mitellastra", genus:="Mitella"]
GenNa[genus=="Mucronea", genus:="Chorizanthe"]
GenNa[genus=="Munroa", genus:="Crypsis"]
GenNa[genus=="Munzothamnus", genus:="Stephanomeria"]
GenNa[genus=="Neoholmgrenia", genus:="Camissonia"]
GenNa[genus=="Noccaea", genus:="Thlaspi"]
GenNa[genus=="Oreocarya", genus:="Cryptantha"]
GenNa[genus=="Oreostemma", genus:="Aster"]
GenNa[genus=="Osmadenia", genus:="Calycadenia"]
GenNa[genus=="Oxytheca", genus:="Eriogonum"]
GenNa[genus=="Pediomelum", genus:="Psoralea"]
GenNa[genus=="Pentachaeta", genus:="Chaetopappa"]
GenNa[genus=="Picradeniopsis", genus:="Bahia"]
GenNa[genus=="Piperia", genus:="Platanthera"]
GenNa[genus=="Pityopus", genus:="Monotropa"]
GenNa[genus=="Pleurocoronis", genus:="Hofmeisteria"]
GenNa[genus=="Podistera", genus:="Ligusticum"]
GenNa[genus=="Poteridium", genus:="Sanguisorba"]
GenNa[genus=="Pseudorontium", genus:="Antirrhinum"]
GenNa[genus=="Sabulina", genus:="Minuartia"]
GenNa[genus=="Saxifragopsis", genus:="Saxifraga"]
GenNa[genus=="Sclerocactus", genus:="Echinocactus"]
GenNa[genus=="Scopulophila", genus:="Achyronychia"]
GenNa[genus=="Scribneria", genus:="Lepturus"]
GenNa[genus=="Sericocarpus", genus:="Aster"]
GenNa[genus=="Sibara", genus:="Arabis"]
GenNa[genus=="Spermolepis", genus:="Apium"]
GenNa[genus=="Sphaeromeria", genus:="Tanacetum"]
GenNa[genus=="Stebbinsoseris", genus:="Microseris"]
GenNa[genus=="Stutzia", genus:="Atriplex"]
GenNa[genus=="Systenotheca", genus:="Chorizanthe"]
GenNa[genus=="Taraxia", genus:="Camissonia"]
GenNa[genus=="Tetraneuris", genus:="Hymenoxys"]
GenNa[genus=="Tetrapteron", genus:="Camissonia"]
GenNa[genus=="Tonestus", genus:="Haplopappus"]
GenNa[genus=="Transberingia", genus:="Halimolobos"]
GenNa[genus=="Tripterocalyx", genus:="Abronia"]
GenNa[genus=="Vahlodea", genus:="Aira"]
GenNa[genus=="Yabea", genus:="Caucalis"]


# Update familes in the mega tree list
setkey(Spp, genus)
setkey(GenNa, genus)
Spp[GenNa,`:=` (genus = i.genus,family=i.Family)]

# Limit to Vascular Plants
SppVas <- Spp[family!="FernOrNonVascular"]

```

# Making and Saving the Tree

Using the S Phylomaker Code to construct phylogenetic tree against species list. 
```{r creating the tree}
# Source the code from Qian & Jin 2016 paper
source("R_codes for S.PhyloMaker.R")

## Bulding Tree for all three scenarios
result_california_tree <- S.PhyloMaker(spList=as.data.frame(SppVas), tree=phylo, nodes=nodes, scenarios=c("S1","S2","S3")) 


```